\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://www.aritropaul.me//}{\Large Aritro Paul}} & Email : \href{mailto:Aritro.Paul2020@uem.edu.in}{Aritro.Paul2020@uem.edu.in}\\
  \href{http://aritropaul.me/}{http://www.aritropaul.me} & Mobile : +91-9007638533 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Engineering and Management}{Kolkata, In}
      {B.Tech Computer Science With Artificial intelligence;  GPA: 8.95}{Aug. 2023}
    \resumeSubheading
      {Kalyani University Experimental High School}{Kalyani, India}
      {Did secondary and higher secondary; (74.40\%/78\%)}{2011 --  2020
      }
  \resumeSubHeadingListEnd


%-----------Projects-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Weathernearme}
      {The weathernearme Project utilizes HTML, CSS and JavaScript along with the OpenWeatherMap API to create an interactive platform for visually exploring real-time weather.}
    \resumeSubItem{Emotion detection using python}
      {facial emotion detection using deep-face library.}
    \resumeSubItem{Personal portfolio website}
      {personal portfolio website using HTML, CSS, JavaScript}
      \resumeSubItem{Responsive admin dashboard}
      {An excellent front-end solution for enterprise applications built upon HTML5, CSS3 and JavaScript}
      \resumeSubItem{online salad ordering website}
      {Using HTML, CSS, and JavaScript, develop this website as a group project during the second year.}

  \resumeSubHeadingListEnd

%-----------Experience-----------------

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Suven Consultants and Technology Pvt.Ltd.}{}
      {Front-End developer}{June 2023 - Present}
      \resumeItemListStart
        \resumeItem{Responsive Admin dashboard}
          {Build a Responsive Admin Dashboard with Bootstrap 4}
        \resumeItem{Responsive website}
          {Create a dynamic website and expand my knowledge of JavaScript by building a responsive site.}
      \resumeItemListEnd
      

    \resumeSubheading
      {Accenture}{}
      {Tecchnology consulting Virtual Experience }{ May 2023 }
      \resumeItemListStart
          
        \resumeItem{Project kickoff}
        {learn about the project objectives, scope, and stakeholders, as well as establish communication channels and initial timelines to ensure a shared understanding and successful project launch.}
          
        \resumeItem{Requirements gathering}
          {gather essential information about the project's desired features, functionalities, and constraints, ensuring a comprehensive understanding of client needs }
        \resumeItem{Voting application design}
          {Learn about essential skills in UI design, user research, information organization, visual design, interaction design.also gain experience in mobile and responsive design, design systems, and project management.}
        \resumeItem{Create agile stories}
          {learn to write concise, user-centric descriptions of desired functionality while adhering to the INVEST criteria and collaborating with stakeholders to define clear acceptance criteria.}
        \resumeItem{Recommendations}
          {Core service for all recommendation systems at Coursesa, currently used on the homepage and throughout the content discovery process. Worked on both offline training and online serving.}
      \resumeItemListEnd

    \resumeSubheading
      {Tata}{}
      {Data Visualisation}{June 2022}
      \resumeItemListStart
        \resumeItem{Framing the Business Scenario}
          {familiarizing with the organization's business, gathering information, analyzing data, identifying problems, developing scenarios, recommending strategies, and communicating findings to stakeholders.}
        \resumeItem{Choosing the Right Visuals}
          {learn visual design principles, data interpretation, and storytelling techniques}
          \resumeItem{Creating Effective Visuals}
          {learn visual design principles, data visualization techniques and also gain experience in branding, UX design and project management.}
          \resumeItem{Communicating Insights and Analysis}
          {gain knowledge about writing, storytelling abilities, active listening, presentation expertise, interpersonal skills, data interpretation, and adaptability}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, JavaScript, SQL, Java, HTML/CSS}
     \hfill
     \textbf{Technologies}{:Microsoft Azure, Google Cloud}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
